---
title: "Joining Review Exercises"
author: "Your Name Here"
date: "`r format(Sys.time(), '%B %d, %Y')`"
format:
  html:
    self-contained: true
    toc: true
    toc-location: left
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(here)

```


# Load the datasets

```{r}

counties_demographics <- readRDS(here("data", "counties_demographics.rds"))
counties_elexresults <- readRDS(here("data", "counties_elexresults.rds"))
counties_rural_urban_suburban <- readRDS(here("data", "counties_rural_urban_suburban.rds"))

head(counties_demographics)
head(counties_elexresults)
head(counties_rural_urban_suburban)

```

# Exercises

Join together the election results and urban/suburban/rural tables above, and then use the merged table to:

-   filter for just Virginia

-   group/summarize to calculate the mean pct of Trump 2020 vote by urban/rural categories

```{r}

big <- inner_join(counties_elexresults, counties_rural_urban_suburban, by = "geoid")

```

```{r}

virginia <- filter(big, state_code == "VA")

virginia %>%
  group_by(rural_urban) %>%
  summarize(avg_trump_vote = mean(pct_r_2020))


```

Now using the joined dataset, come up with two groupings you find interesting or newsworthy in a particular state, and replicate the steps above them them instead.

(i.e. instead of for urban/rural, perhaps you want to look at pct of white college grads in Michigan, etc. If you're having trouble, you can stick with Virginia as your state.)

```{r}

big %>%
  filter(state_code == "TX") %>%
  group_by(rural_urban) %>%
  summarize(dem_voter_percent = mean(pct_d_2020 - pct_d_2016))
  


```


```{r}

big %>%
  filter(state_code == "VA") %>%
  group_by(rural_urban) %>%
  summarize(republican_voter_percent = mean(pct_r_2020 - pct_r_2016))



```
